---
output: # choose either word_document or html_document
  #html_document
  word_document:
    reference_docx: word-styles-reference.docx
params:
  #mond: !r monitor    # Monitoring data   (uncomment for interactive use)
  #mand: !r manage     # Management data   (uncomment for interactive use)
  #moni: !r mon_issues # Monitoring issues (uncomment for interactive use)
  #mani: !r man_issues # Management issues (uncomment for interactive use)
  #ce:   2020          # Second/Final year of the cycle (for interactive use)
  mond: NULL # Monitoring data
  mand: NULL # Management data
  moni: NULL # Monitoring issues
  mani: NULL # Management issues
  ce:   NULL # Second/Final year of the cycle
---

```{r source, include=FALSE}
## Uncomment this section to knit from console rather than through app.R

## Source the functions (only needed if you want to run this script on its own)
# source("./src/review-reports/checkbox-functions.R")

## the render command, if you need to generate the report directly:
# rmarkdown::render("report.RMD", params=list(mond=mon_data, mand=man_data, moni=mon_issues, mani=man_issues, ce=2018))
# make sure that mon_data, man_data, mon_issues, man_issues are loaded & enter
# the year you want
# man_data is assumed to already have the application dates merged in
# The rendered file is called report.docx and it's written to the working
# directory
```

``` {r title, results = 'asis', echo=FALSE}
cat("# Reports with possible issues: ", params$ce - 1, "-", params$ce, " Cycle", sep = "")
cat("  \n")
cat("#### *Date generated:", as.character(Sys.Date()), "*")
```

Not all reports submitted through the Web Hub contain information that the PAMF 
model can use. In many cases, we cannot sort usable from unusable reports using automated methods (e.g. when there's disqualifying information in a 'notes' 
field). PAMF's interactive UI has flagged all reports from this cycle that 
require your judgement, and will prompt you for decisions about whether they 
should be passed on to different parts of the PAMF model.

**This document is a preview of what you'll see on PAMF's interactive UI checkbox screen.**
It allows you to look through the flagged reports at your own pace, without 
having to keep the UI open as you work through the list.

**Tips and tricks:**

* To view without page breaks in Word, select "Web Layout" from the "View" ribbon.
* Use the decision keys below each report to keep track of exclusions.
* You can annotate this document by adding comments.
* You can close the UI and return to it later, without losing any information 
about which reports need your attention. Reports with saved decisions at the 
time that you close the UI, however, will not display again unless you initiate 
a different model run. This is to prevent different decisions from being applied 
to the same report at different times.
* If you believe that the content of any report should be changed, contact the 
participant and make the changes through the Web Hub. To make these changes 
visible to the PAMF model, conduct another database pull and initiate a model run
on the new download. This process is cumbersome, but it's important for reproducibility that we maintain a single centralized version of the data.
* Reports without issues that need human judgement are not displayed in this document.

 \newline 
 
***


```{r calculate, include=FALSE}
## Get information needed for display, but don't display it yet
#  In the final document, information about reports with possible issues will be
#  grouped by management unit, with two sub-headings: Monitoring Reports and
#  Management Reports.
#
#  Each sub-section will:
#    * only appear if it is non-empty (one or more reports have possible issues)
#    * contain a list of possible issues followed by relevant information from
#      the reports (e.g. notes; a table with stem counts)

## 1. Management Unit IDs

# First, find the munitids and report ids of reports with possible issues & sort
# by munitid
# then monitorid to reflect the way that possible issues will be displayed
flagged_mon <- getFlaggedMon(params$moni, params$ce)
flagged_mon <- flagged_mon[order(flagged_mon$munitid, flagged_mon$monitorid), ]
flagged_man <- getFlaggedMan(params$mani, params$ce)
flagged_man <- flagged_man[order(flagged_man$munitid, flagged_man$treatmentid), ]

# Get munitids that have at least one associated report with a potential issue
flagged_mu <- union(flagged_mon$munitid, flagged_man$munitid)
flagged_mu <- flagged_mu[order(flagged_mu)]


## 2. Monitoring reports with possible issues
# Get a list of messages describing the possible issues with each report
describe_issues_mon <- lapply(flagged_mon$monitorid, getMonFlags, params$moni)


## 3. Management report with possible issues
# Get a list of messages describing the possible issues with each report
describe_issues_man <- lapply(flagged_man$treatmentid, getManFlags, params$mani)

# Extract notes from management reports. Since there are close to 30 notes
# fields in each report, put them into three categories: management action notes,
# product/equipment notes, and guidance compliance notes.
#
# First, pull up the management reports associated with man_flagged$treatmentid,
# and put them into display order.
mand_flagged <- params$mand[params$mand$treatmentid %in% flagged_man$treatmentid, ]
mand_flagged <- mand_flagged[order(mand_flagged$munitid, mand_flagged$treatmentid), ]

# Second, keep only the first row with each treatmentid. Multiple rows with the
# same treatmentid belong to the same report and only vary in their application
# information, which we don't use in this step.
mand_flagged <- mand_flagged[which(!duplicated(mand_flagged$treatmentid)), ]

# Then, since the functions that extract the notes each take a single row
# of the report table, break the dataframe into a list of rows
fm_rows <- split(mand_flagged, seq(nrow(mand_flagged)))

ma_notes <- lapply(fm_rows, getMAnotes)
pe_notes <- lapply(fm_rows, getPEnotes)
gc_notes <- lapply(fm_rows, getGCnotes)

## If knitting to word_document, replace all instances of <br> in the *_notes
#  lists with "  \n"
#  These lists are generated for the checkbox interface, which uses <br> as a
#  line break; however word documents recognize "\n" instead
if (rmarkdown::all_output_formats(knitr::current_input()) == "word_document") {
  describe_issues_mon <- gsub("<br>", "  \n", describe_issues_mon)
  describe_issues_man <- gsub("<br>", "  \n", describe_issues_man)

  ma_notes <- gsub("<br>", "  \n", ma_notes)
  pe_notes <- gsub("<br>", "  \n", pe_notes)
  gc_notes <- gsub("<br>", "  \n", gc_notes)
}
```

```{r display, echo=FALSE, results="asis", strip.white=FALSE}
# Display munitids iteratively
for (fm in flagged_mu) {
  cat("# **Management Unit", fm,  " - ", enroll_data[enroll_data$munitid == fm, "name"], "**{-}  \n")
  cat("  \n\n")

  ## Get flagged reports associated with the MU
  mon_ids <- flagged_mon[flagged_mon$munitid == fm, "monitorid"]
  man_ids <- flagged_man[flagged_man$munitid == fm, "treatmentid"]

  ## Display Monitoring Reports
  if (length(mon_ids > 0)) {
    cat("## Monitoring Reports {-}  \n")
    cat("  \n\n")
    for (m in mon_ids) {
      cat("### **Monitoring Report", m, "** {-}  \n")

      ## Describe possible issues
      cat("**Possible Issues:  \n**")
      report_index <- which(flagged_mon$monitorid == m)
      cat(describe_issues_mon[[report_index]])
      cat("  \n\n")

      ## Display notes
      cat("**Notes:  \n**")
      cat(params$mond[params$mond$monitorid == m, "notes"])
      cat("  \n\n")

      ## Display relevant information from the report
      print(knitr::kable(params$mond[
        params$mond$monitorid == m,
        c(
          "dateentered", "monitoringdate",
          "establishment", "q1stemcount",
          "q2stemcount", "q3stemcount",
          "q4stemcount", "q5stemcount", "userid"
        )
      ],
      col.names = c(
        "date entered", "monitoring date",
        "establishment", "q1 stem count",
        "q2 stem count", "q3 stem count",
        "q4 stem count", "q5 stem count",
        "user ID"
      ),
      row.names = FALSE
      ))
      cat(" \n")

      ## Display name/date space to keep track of who reviewed the report and when
      cat("  \n")
      cat("**Reviewed By:  \n**")
      cat("  \n")
      cat("**Review Date:  \n**")
      cat("  \n")

      ### Display the checkbox options that the UI user will see
      cat("**Decisions:  **")
      print(knitr::kable(data.frame(
        choices = c(
          "Exclude from Transition Matrix Update",
          "Exclude from Guidance and Transition Matrix Update",
          "Exclude from Annual Summary",
          "Exclude from Post-hoc Analysis"
        ),
        entries = c("____", "____", "____", "____")
      ),
      col.names = c(" ", " "),
      row.names = FALSE
      ))
      cat("  \n")
    } # end loop through monitoring reports
    cat("  \n\n")
  } # end conditional (display monitoring reports)

  ## Display Managment Reports
  if (length(man_ids > 0)) {
    cat("## Management Reports {-}  \n")
    cat("  \n\n")
    for (m in man_ids) {
      cat("### **Management Report", m, "** {-}  \n")

      ## Describe Possible Issues
      cat("**Possible Issues:  \n**")
      report_index <- which(flagged_man$treatmentid == m)
      cat(describe_issues_man[[report_index]])
      cat("  \n\n")

      ## Display notes
      cat("**Management Action Notes:  \n**")
      cat(ma_notes[[report_index]])
      cat("  \n\n")
      cat("**Product/EquipmentNotes:  \n**")
      cat(pe_notes[[report_index]])
      cat("  \n\n")
      cat("**Guidance Compliance Notes:  \n**")
      cat(gc_notes[[report_index]])
      cat("  \n\n")

      ## Display relevant information from the report
      #  Depending on the year, display with either managementdate or dateentered
      if (params$ce < 2020) {
        print(knitr::kable(params$mand[
          params$mand$treatmentid == m,
          c(
            "managementdate", "treatmethod",
            "phase", "munitcondition", "floodmonths",
            "applicationdate"
          )
        ],
        col.names = c(
          "management date", "action", "phase",
          "hydro condition", "flood months",
          "application date"
        ),
        row.names = FALSE
        ))
      } else {
        print(knitr::kable(params$mand[
          params$mand$treatmentid == m,
          c(
            "dateentered", "treatmethod",
            "phase", "munitcondition", "floodmonths",
            "applicationdate"
          )
        ],
        col.names = c(
          "date entered", "action", "phase",
          "hydro condition", "flood months",
          "application date"
        ),
        row.names = FALSE
        ))
      }

      cat("  \n")

      ## Display name/date space to keep track of who reviewed the report and when
      cat("  \n")
      cat("**Reviewed By:  \n**")
      cat("  \n")
      cat("**Review Date:  \n**")
      cat("  \n")

      ### Display the checkbox options that the UI user will see
      cat("**Decisions:  **")
      print(knitr::kable(data.frame(
        choices = c(
          "Exclude from Transition Matrix Update",
          "Exclude from Cost Calculation",
          "Exclude from Annual Summary",
          "Exclude from Post-hoc Analysis"
        ),
        entries = c("____", "____", "____", "____")
      ),
      col.names = c(" ", " "),
      row.names = FALSE
      ))
      cat("  \n")
    } # end loop through management reports
    cat("  \n")
  } # end conditional (display management reports)
  cat("  \n")
  cat("***")
  cat("  \n  \n  \n")
} # end for
```
