---
date: "May 7, 2020"
output: word_document
## NOTE: Rendering this file without specifying a file name will overwrite the current style document.
#        This re-sets the file to default style settings: All manual changes will be LOST!
---

```{r setup, include=FALSE}
## Set global options
```

## Coordinator QAQC Report 
### Style Reference Document

Some information:

* This document contains a simplified mock-up of the QAQC report structure (one management unit, with one monitoring and management report each)
* The actual QAQC reports pull their style information from this document. To change the style of those, change the styles here
* I used the following instructions for modifying styles: https://rmarkdown.rstudio.com/articles_docx.html ("Happy collaboration with Rmd to docx")
* No styles have been changed from the default settings as of 2020-05-07

***

```{r variables, include=FALSE}
## Generate the variables that will be populated into the report mock-up

munitid <- 123 # ID of management unit
monitorid <- 45 # ID of monitoring report
treatmentid <- 67 # ID of management report

## Descriptions of possible issues
monissues <- "Issue 1 <br> Issue 2 <br> Issue 3 <br> There are notes to review <br>"
manissues <- "Issue 4 <br> Issue 5 <br> Issue 6 <br> There are notes to review <br>"

## Notes
monnotes <- "Unfortunately this Management Unit is totally made up. It doesn't even exist. I went ahead and monitored it anyway, hope that's OK"

mannotes_ma <- "I only treated 1/3 of the area. There was no biomass to leave" # Management Action Notes
mannotes_pe <- "Marsh Master vs. TRUXOR: Who would win?" # Product/Equipment Notes
mannotes_gc <- "I forgot my password and don't remember the guidance" # Guidance Compliance Notes

## Monitoring report
# Note that in this and the management report, some of the values have been converted to text for
# readability (e.g. establishment="0-10%", phase="Dormant"). This occurs in an earlier step in the model.
monitor <- data.frame(
  datentered = "2020-07-30",
  monitoringdate = "2020-07-24",
  establishment = "11-50%",
  q1stemcount = 3,
  q2stemcount = 4,
  q3stemcount = 5,
  q4stemcount = 6,
  q5stemcount = 7,
  userid = 99
)

## Management report
#  Note that this dataframe reflects a management report with more than one application date. The
#  management and application tables (from the database) are merged in an earlier step, resulting in
#  multi-line management reports where more than one application date was entered.
manage <- data.frame(
  managementdate = c("2020-02-02", "2020-02-02"),
  treatmethod = c("Mechanical & Leave Biomass", "Mechanical & Leave Biomass"),
  phase = c("Dormant", "Dormant"),
  applicationdate = c("2020-01-01", "2020-01-31")
)
```

``` {r display, echo=FALSE, results='asis'}
## I'm trying to keep as close as possible to the formatting commands in report.Rmd as of 2020-05-07,
#  while leaving out the for loops. variable names are changed.

## Management Unit
cat("### **Management Unit", munitid, " - ", name, "**{-}  \n")
cat("  \n\n")

## Monitoring Report

cat("### Monitoring Reports {-}  \n")
cat("  \n\n")

cat("#### **Monitoring Report", monitorid, "** {-}  \n")

# Display Issues
cat("**Possible Issues:  \n**")
cat(monissues)
cat("  \n\n")

# Display notes
cat("**Notes:  \n**")
cat(monnotes)
cat("  \n\n")

# Display relevant information from the report
print(knitr::kable(monitor,
  col.names = c(
    "date entered", "monitoring date", "establishment", "q1 stem count",
    "q2 stem count", "q3 stem count", "q4 stem count", "q5 stem count", "user ID"
  ),
  row.names = FALSE
))
cat("  \n\n\n")
cat("  \n")

## Management Report

cat("### Management Reports {-}  \n")
cat("  \n\n")
cat("#### **Management Report", treatmentid, "** {-}  \n")

# Display issues
cat("**Possible Issues:  \n**")
cat(manissues)
cat("  \n\n")

# Display notes
cat("**Management Action Notes:  \n**")
cat(mannotes_ma)
cat("  \n\n")
cat("**Product/EquipmentNotes:  \n**")
cat(mannotes_pe)
cat("  \n\n")
cat("**Guidance Compliance Notes:  \n**")
cat(mannotes_gc)
cat("  \n\n")

# Display relevant information from the report
print(knitr::kable(manage, row.names = FALSE))
cat("  \n\n\n")

cat("***")
cat("  \n")
```
